Response to reviewers

### 2024-11-28 Manuscript/main_ecography_R1.tex
Update main_ecography_R1.tex

For example, say one is interested in looking at changes in functional diversity using a divergence metric using the probability density method (e.g. \texttt{TPD::REND}).
They can then apply this metric to their trait space and get two relative metric scores of, says, 0.7 and 0.65 (pattern) for two levels of extinction (process).
The interpretation of this score as a change in functional diversity will depend on the worker's assumption of which mechanism affected the trait space.
In our simulations, if the mechanism approximated was the equalising one, the pattern can clearly be interpreted as a change in functional diversity, but if the mechanism is a facilitation one, the pattern can be meaningless (i.e. not clearly distinguishable from a null mechanism - Fig. \ref{Fig:simulation_results} shows this example by contrasting row 5, columns 1 and 2).
In this made up example, the procedure is done in reverse order where the the pattern is specified first and then the process and the mechanism (``What process and mechanism are needed to interpret pattern X?'').
In Box 2 we suggest an approach that specifies the process and the mechanism first (``how do I interpret pattern X under a specific process and mechanism''; see Box 2).

>>>>

For example, say one is interested in looking at changes in functional diversity using a divergence metric calculated with the probability density method (e.g. \texttt{TPD::REND}).
They can apply this metric to their trait space and get two relative metric scores of, say, $0.7$ and $0.65$ (pattern) for two levels of extinction (process).
The interpretation of this score as a change in functional diversity will depend on the worker's assumption of which mechanism affected the trait space.
In our simulations, if the mechanism approximated was the equalising one, the pattern can clearly be interpreted as a change in functional diversity, but if the mechanism is a facilitation one, the pattern can be meaningless (i.e. not clearly distinguishable from a null mechanism - Fig. \ref{Fig:simulation_results} shows this example by contrasting row 5, columns 1 and 2).
In this made up example, the procedure is done in reverse order where the the pattern is specified first and then the process and the mechanism (``What process and mechanism are needed to interpret pattern X?'').
In Box 2 we suggest an approach that specifies the process and the mechanism first (``how do I interpret pattern X under a specific process and mechanism''; see Box 2).
